Hierarchical Large Language Models for Multi-task problems

### 2024-02-18 paper/main.tex
minor
add results

\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\usepackage{amsmath}
\addbibresource{references.bib}

@@

\section{Related works}
\begin{itemize}
    \item explain what pretraining LLM means
    \item Explain how LORA fine tuned is done on each task
    \item Explain how LORA finetuned also could be done on all tasks together if they have a similar data distribution.
\end{itemize}

@@

\subsection{Task and Data Structure}
We define our study across $D$ distinct tasks, denoted as $d=1,2,...,D$. For each task, our dataset comprises $N_d$ documents, with each document containing a sequence of $W_n$ tokens. This dataset structure is pivotal for our analysis and can be formally represented as:

\begin{equation} \label{eq:data}
\mathcal{D} = \{{ w_{d,n,1:W_n} }{n=1}^{N_d} \}_{d=1}^D
\end{equation}

@@

>>>>

\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\usepackage{amsmath}
\usepackage{booktabs}
\addbibresource{references.bib}

@@

\section{Related works}
[This might be background?]
\begin{itemize}
    \item explain what pretraining LLM means
    \item Explain how LORA fine tuned is done on each task
    \item Explain how LORA finetuned also could be done on all tasks together if they have a similar data distribution.
\end{itemize}

@@

\subsection{Task and Data Structure}
We define our study across $D$ distinct tasks, denoted as $d=1,2,...,D$. For each task, our dataset comprises $N_d$ documents, with each document containing a sequence of $W_n$ tokens. This dataset structure can be formally represented as:

\begin{equation} \label{eq:data}
\mathcal{D} = \{ \{ w_{d,n,1:W_n} \}_{n=1}^{N_d} \}_{d=1}^D
\end{equation}

@@

\section{Results}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{figures/results_plot.png}
    \caption{Plot of Regularization Constant vs Perplexity}
    \label{fig:results_plot}
\end{figure}

\begin{table}[h]
\centering
\caption{Empirical results of the hierarchical LORA finetuned on the three tasks. The perplexity is calculated on the validation set.}
\label{tbl:results}
\begin{tabular}{ccc}
    \toprule
    Learning Rate & Regularization & Validation Perplexity \\
    \midrule
        $10^{-4}$ &              0 &                 16.80 \\
        $10^{-5}$ &       $10^{0}$ &                 16.59 \\
        $10^{-4}$ &       $10^{1}$ &                 12.85 \\
        $10^{-3}$ &       $10^{2}$ &                 \textbf{12.82} \\
        $10^{-2}$ &       $10^{3}$ &                 13.26 \\
        $10^{-1}$ &       $10^{4}$ &                 13.91 \\
    \bottomrule
    \end{tabular}
\end{table}
